
\section{Problem Description}
Blockchain is a type of database and storage that is decentralized, reliable, and difficult to use for fraudulent purposes. On the other hand, bitcoin and other digital currencies use a blockchain general ledger to trade in peer-to-peer networks.
Bitcoin and blockchain technology have begun to shape and define new aspects of computer science and information technology. The need for decentralized currency, apart from government control and manipulation, has long been a theory of languages, but has been realized in the last decade thanks to Satoshi Nakamato's famous article in 2007 and the introduction of blockchain technology.
While there is controversy over Nakamato's true identity, he has undoubtedly introduced the world's largest and most revolutionary technology after the Internet. Users now have to decide what they want to do with it. Some take this opportunity and develop their own app to solve various problems and holes in the community. Some are either investing in those ideas or making money with the waves and rising crypto prices.
Merely the peer-to-peer version of electronic cash allows direct online payment from one side to the other without the institution of a financial institution. For this problem we propose transfers from peer to peer.
The research seeks to find out the blockchain structure of how it works and build a Crypto to compete in international crypto markets, as well as fix current banking transaction security problems, eliminate transparency, reduce transaction costs and prevent financial crime. In addition to the aforementioned, it is creating jobs such as building a farm for drilling and needing a developer to build and continue developing these Crypto and Blockchain networks. Of course, one should not overlook the fact that this very new technology is complementing itself and having some drawbacks, but working on them can fix these problems. Despite all the current problems, it is superior to Fiat currencies.

\section{Research Motivations}
Building a national CryptoCurrency with the aim of making it publicly available in the Iranian market and in foreign countries to facilitate and streamline transactions.

\section{Research Objectives}
\begin{enumerate}
\item Building nodes and BlockChain Network On a CLI interface
\item Build node on web platform and browser
\item Build blockchain modules
\item Creating Wallets
\item Constructing a mining method for our Blockchain
\item Developing resolving conflict method
\item Fixing bugs and optimizing the code
\item Providing the application on git for further development

\end{enumerate}
